\textbf{\sc Towards Deliberative Control of Autonomous Robots}

### 2012-01-18 setobook.tex
update

\title*{\textbf{\sc Deliberative Autonomy for Marine Robotics}}
\author{\normalsize Kanna~Rajan\inst{1} \and Fr\'ed\'eric Py\inst{1}
  \and Javier Barreiro\inst{2}}
\institute{Monterey Bay Aquarium Research Institute, California
  \texttt{\{Kanna.Rajan,fpy\}@mbari.org}
  \and
  NASA Ames Research Center, Moffett Field, California
  \texttt{javier.barreiro@nasa.gov}}
% \date{\small Monterey Bay Aquarium Research Institute \\
% 7700 Sandholdt Rd.\\
% Moss Landing,  CA, 95039\\
% {\tt }}

@@

The authors are funded by a block grant from the David and Lucile
Packard Foundation to MBARI.

>>>>

\titlerunning{Towards Deliberative Control of Autonomous Robots}
\authorrunning{K.Rajan et. al.}

\title*{\textbf{\sc Towards Deliberative Control of Autonomous Robots}}
\author{\normalsize Kanna~Rajan\inst{1} \and Fr\'ed\'eric Py\inst{1}
  \and Javier Barreiro\inst{2}}
\institute{Monterey Bay Aquarium Research Institute, California
  \texttt{\{Kanna.Rajan,fpy\}@mbari.org}
  \and
  NASA Ames Research Center, Moffett Field, California
  \texttt{javier.barreiro@nasa.gov}}

@@

Authors Rajan and Py are funded by a block grant from the David and
Lucile Packard Foundation to MBARI.
